Outputs - civil servants' survey

### 2024-12-02 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd
Updating regression tables and main models

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior)

@@

@@

#work effort
0.2787879/0.1746032
```
## Model prediction

```{r}
pd_data <- data.frame(BACKSLIDING_2 = seq(0, 1, length = 100),
                 PAST_POLITICIZATION = rep(mean(data_for_analysis_senior$PAST_POLITICIZATION,na.rm=T), length = 100),
                 PAST_INFLUENCE = rep(mean(data_for_analysis_senior$PAST_INFLUENCE,na.rm=T), length = 100),
                 PAST_VOICE = rep(mean(data_for_analysis_senior$PAST_VOICE,na.rm=T), length = 100),
                 PAST_EFFORT = rep(mean(data_for_analysis_senior$PAST_EFFORT,na.rm=T), length = 100))

pd_data_exit <- pd_data %>% 
  cbind(predict(exit_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
  transform(
    Upper = fit + (1.96 * se.fit),
    Lower = fit - (1.96 * se.fit))

pd_data_voice <- pd_data %>% 
  cbind(predict(voice_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
  transform(
    Upper = fit + (1.96 * se.fit),
    Lower = fit - (1.96 * se.fit))

pd_data_work <- pd_data %>% 
  cbind(predict(work_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
  transform(
    Upper = fit + (1.96 * se.fit),
    Lower = fit - (1.96 * se.fit))

```{r,fig.width=10,fig.height=4}
p1 <- data_for_analysis_senior %>% 
  ggplot(aes(x=BACKSLIDING_2,y=INTENT_EXIT_2))+
  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
  labs(x="Perceived democratic backsliding",
       y="Exit intention")+
  #geom_smooth(method="lm")+
    geom_line(data = pd_data_exit, aes(y = fit, x = BACKSLIDING_2),size=2) +
  geom_line(
    data = pd_data_exit,
    aes(y = Lower),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  geom_line(
    data = pd_data_exit,
    aes(y = Upper),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  theme_classic()

p2 <- data_for_analysis_senior %>% 
  ggplot(aes(x=BACKSLIDING_2,y=PROJECT_VOICE))+
  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
  labs(x="Perceived democratic backsliding",
       y="Voice intention")+
  #geom_smooth(method="lm")+
    geom_line(data = pd_data_voice, aes(y = fit, x = BACKSLIDING_2),size=2) +
  geom_line(
    data = pd_data_voice,
    aes(y = Lower),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  geom_line(
    data = pd_data_voice,
    aes(y = Upper),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  theme_classic()

p3 <- data_for_analysis_senior %>% 
  ggplot(aes(x=BACKSLIDING_2,y=PROJECT_EFFORT))+
  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
  labs(x="Perceived democratic backsliding",
       y="Work effort intention")+
  #geom_smooth(method="lm")+
    geom_line(data = pd_data_work, aes(y = fit, x = BACKSLIDING_2),size=2) +
  geom_line(
    data = pd_data_work,
    aes(y = Lower),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  geom_line(
    data = pd_data_work,
    aes(y = Upper),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  theme_classic()

ggpubr::ggarrange(p1,p2,p3,
          ncol=3,
          label.x = "Perceived democratic backsliding")
```

# Exit 1

@@

sjPlot::tab_model(politicization_mod1,politicization_mod1_relig,
                  influence_mod1,influence_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)#,
                  dv.labels = c("Expected politicization","Expected influence")#,
                  #order.terms = c(2:4,1)
                  )

@@

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            #BACKSLIDING_2 +   
              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
            data=data_for_analysis_senior)
exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)

>>>>

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

@@

## SEM models

```{r}
SEM_All <-'

##Direct effects##
INTENT_EXIT_2 ~ cp_ex*BACKSLIDING_2
PROJECT_VOICE ~ cp_vc*BACKSLIDING_2 + PAST_VOICE
PROJECT_EFFORT ~ cp_eff*BACKSLIDING_2 + PAST_EFFORT

##Mediators##
PROJECT_POLITICIZATION ~ a1*BACKSLIDING_2 + PAST_POLITICIZATION 
PROJECT_INFLUENCE ~ a2*BACKSLIDING_2 + PAST_INFLUENCE

INTENT_EXIT_2 ~ b1_ex*PROJECT_POLITICIZATION + PAST_POLITICIZATION
INTENT_EXIT_2 ~ b2_ex*PROJECT_INFLUENCE + PAST_INFLUENCE

PROJECT_VOICE ~ b1_vc*PROJECT_POLITICIZATION + PAST_POLITICIZATION
PROJECT_VOICE ~ b2_vc*PROJECT_INFLUENCE + PAST_INFLUENCE

PROJECT_EFFORT ~ b1_eff*PROJECT_POLITICIZATION + PAST_POLITICIZATION
PROJECT_EFFORT ~ b2_eff*PROJECT_INFLUENCE + PAST_INFLUENCE

## Indirect effects ##
tot_ind_exit := abs(a1*b1_ex) + abs(a2*b2_ex)
tot_ind_voice := abs(a1*b1_vc) + abs(a2*b2_vc)
tot_ind_effort := abs(a1*b1_eff) + abs(a2*b2_eff)

dir_backs_polit := a1
dir_backs_inf := a2

dir_backs_exit := cp_ex
dir_polit_exit := b1_ex
dir_infl_exit := b2_ex

dir_backs_voice := cp_vc
dir_polit_voice := b1_vc
dir_infl_voice := b2_vc

dir_backs_effort := cp_eff
dir_proj_polit_effort := b1_eff
dir_proj_infl_effort := b2_eff

##indirect effects##
ind_back_polit_exit := a1*b1_ex
ind_back_infl_exit := a2*b2_ex

ind_back_polit_voice := a1*b1_vc
ind_back_infl_voice := a2*b2_vc

ind_back_polit_effort := a1*b1_eff
ind_back_infl_effort := a2*b2_eff

##total effects##
tot_back_exit := cp_ex + (a1*b1_ex) + (a2*b2_ex)
tot_back_voice := cp_vc + (a1*b1_vc) + (a2*b2_vc)
tot_back_effort := cp_eff + (a1*b1_eff) + (a2*b2_eff)

##Correlations between mediators##
PROJECT_POLITICIZATION~~PROJECT_INFLUENCE

##Other correlations##
PROJECT_POLITICIZATION~~PAST_INFLUENCE
PROJECT_INFLUENCE~~PAST_POLITICIZATION
PAST_POLITICIZATION~~PAST_INFLUENCE
PAST_EFFORT~~PROJECT_POLITICIZATION
PAST_EFFORT~~PROJECT_INFLUENCE

##Contrasts
c1v2_exit := (a1*b1_ex) - (a2*b2_ex)
c1v2_voice := (a1*b1_vc) - (a2*b2_vc)
c1v2_effort := (a1*b1_eff) - (a2*b2_eff)'

fit_all <- sem(SEM_All, # model formula
                se = "bootstrap",
                missing="ML",
                data = data_for_analysis_senior)# 
```

```{r}
summary(fit_all, fit.measures=TRUE, standardized=TRUE)
```

```{r}
parameterEstimates(fit_all, boot.ci.type	="basic", standardized = T, output = "text")
```

# Online appendix

@@

#work effort
0.2787879/0.1746032
```

## Exit 1

@@

sjPlot::tab_model(politicization_mod1,politicization_mod1_relig,
                  influence_mod1,influence_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)#,
                  dv.labels = c("Expected politicization","Expected influence")

@@

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   
              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
            data=data_for_analysis_senior)
exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)
